%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Full-Stack Consultant} % Job title
    {Aeler Technologies Sa} % Organization
		{UPTEC, Porto, Portugal (Remote)} % Location
    {Dec. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building cutting-edge cloud based logistic solutions for the container shipping industry.}
        \item {Was responsible for: Developing features and Designing architectures as part of Cloud Software Team.}
	\item {Provisioned and Managed on-premise development and production environments utilizing gitlab, docker, linux servers and AWS environments.}
        \item {Built fully automated CI/CD pipelines on GitLab-CI for containerized applications using Docker.}
				\item {Designed versatille distribute architectures that could scale with project demands and client requirements.}
        \item {Implemented TypeScript+NodeJs fullstack applications.}
        \item {Explored Kubernetes based API-Gateway software solutions for the whole software production stack: Design, Deploy, Maintenance/Monitoring}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Team Lead} % Job title
    {Digital Microscopy Applications - IPATIMUP} % Organization
    {I3S, Porto, Portugal} % Location
    {Nov. 2017 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building a suite of real-time collaborative tools and services, developing a digital microscopy and information systems platform, to aid in the diagnosis of Oncologic Pathologies. }
        \item {Was responsible for: a team of 6 developers; designing features and architecture; approving specifications and code.}
	\item {Provisioned and Managed on-premise development and production environments utilizing gitlab, docker, and several linux servers.}
        \item {Built fully automated CI/CD pipelines on GitLab-CI for containerized applications using Docker.}
        \item {Designed several client-server architecture applications and pipelines around Digital Microscopy Services.}
        \item {Implemented ReactJS+TypeScript applications alongside with Go and Python backends.}
        \item {Deployed a centralized monitoring environment (NetData, Prometheus, Grafana) which gather system metrics as well as docker run-time metrics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python Developer} % Job title
    {Opsview} % Organization
    {Reading, England} % Location
    {Sep. 2015 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building a high-concurrency, distributed server monitoring engine.}
        \item {Implemented Python components in messaged based, fully scalable, architecture.}
	\item {Built Vagrant+Ansible pipeline to provision virtual machines for the development teams.}
	\item {Migrated specifications and business logic from the previous codebase (perl) to Python.}
        \item {Was responsible for code-reviewing junior cowokers Python code and for helping them transitions skills from Perl to Python.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Software Team Lead} % Job title
    {BEEVERYCREATIVE - 3D Printing} % Organization
    {Aveiro, Portugal} % Location
    {Jun. 2013 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Was promoted to department lead retaining all previous tasks/responsibilities.}
        \item {Was responsible for: a team of 3 developers and several contractors; designing features and architecture; approving specifications and code.}
        \item {Was responsible for writting job specifications and interviewing applicants for the software team.}
	\item {Was responsible for coordinating releases with marketing and product development.} 
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Software Engineer} % Job title
    {BEEVERYCREATIVE - 3D Printing} % Organization
    {Aveiro, Portugal} % Location
    {May. 2012 - May. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed open-source java based 3D printing applications.}
        \item {Developed open-source 3D printing firmware.}
	\item {Built a hardware\&software testing aparatus for QA small scalle 3Dprinter manufacture.}
        \item {Developed methodology and software testing tools for mechanics and design teams.}
        \item {Worked on product design, product development, and QA processes.}
      \end{cvitems}
    }

%---------------------------------------------------------

%  \cventry
%    {Django Web Developer} % Job title
%    {Self-Employed} % Organization
%    {Porto, Portugal} % Location
%    {Sep. 2011 - Apr. 2012} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Developed small Django web applications for private customers.} 
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
