%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentation}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------

  \cventry
   {Presenter for Criteria Marathon: A new way to interact with Digital Slides} % Role
   {Web Summit 2019} % Event
   {Lisbon, Portugal} % Location
   {Nov 2019} % Date(s)
   {
     \begin{cvitems} % Description(s)
       \item {Introduced my company (Criteria Marathon) to investors and clients and pitched our solution in Whole-Slide Imaging}
     \end{cvitems}
   }

%---------------------------------------------------------
  \cventry
    {Presenter for porto.codes : Back from the Future of Computing.} % Role
    {porto.codes Meetup Group} % Event
    {Porto, Portugal} % Location
    {Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced the Future of Competing Summer School to the porto.codes community.}
        \item {Talked about  my experience attending the FoC2019 and past experiences with the Data Science Portugal Community.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Presenter for Make or Break: Introduction to 3D Printing and Parametric Design.} % Role
    {Make or Break 2017} % Event
    {Porto, Portugal} % Location
    {Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduction to the essentials of 3D printing and parametric design.}
	\item {Conducted a workshop on 3D design and printed some samples.}	
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Presenter for porto.codes : Concurrent Python made (near) painless using gevent.} % Role
    {porto.codes Meetup Group} % Event
    {Porto, Portugal} % Location
    {Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced principle of concurrency in the python language.}
        \item {Performed a live-coding session demonstrating python co-routine techniques using gevent.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
